Simple repression draft

### 2020-05-21 doc/section_05_discussion.tex
Added to constit prom Bayesian inference + minor file reorg

>>>>

It is interesting to speculate what microscopic details are being
coarse-grained by our burst rate and burst size in model 5.
Chromosomal locus is one possible influence we have not addressed
in this work, as all the FISH data from~\cite{Jones2014} that we
considered was from a construct integrated at the \textit{galK} locus.
The results of~\cite{Chong2014} indicate that
transcription-induced supercoiling contributes substantially in
driving transcriptional bursting, and furthermore, their Figure~7
suggests that the parameters describing the rate, duration, and
size of bursts vary substantially for transcription from
different genomic loci.
Although the authors of~\cite{Englaender2017} do not address
noise, they note enormous differences in mean expression levels
when an identical construct is integrated at different genomic loci.
The authors of~\cite{Engl2020} attribute noise and burstiness in
their FISH data to the influence of different sigma factors,
which is a reasonable conclusion from their data.
Could the difference also be due to the different chromosomal
locations of the two operons?

It seems clear therefore that chromosomal locus plays a major
role in mean expression levels as well as noise. What features of
different loci are and are not important? Sigma factors could
certainly play a part, but it seems many other mechanisms are at
play: supercoiling, and more generally 3D organization of the
chromosome, read-through of neighboring genes, and surely some
fascinating unknown unknowns.
Could our preferred coarse-grained model capture the variability
across different loci? If so, and we were to repeat the parameter
inference as done in this work, is there a simple theoretical model
we could build to understand the resulting parameters?

A direct \mmnote{if cloning intensive} future experiment would be
to design a payload with a promoter driving a FISH reporter,
integrate that payload at a variety of loci scattered around the genome,
and carry out FISH measurements of the resulting strains.
\mmnote{
Did Brewster already do this? I remember he integrated arrays of
competitor binding sites all over the genome, but did he put
lacUV5 + reporter scattered around?}
Obviously integration loci would need to be carefully chosen so
that one could plausibly hope the deletion and integration did
not disturb the cell's physiology too badly.
